### 2020-02-21 doc/icfp20/intro.tex
put abstract in a separate file; fix typo

Edgar Var\`{e}se describes music as ``organized sound'', and
throughtout history cultures have created and applied systems of rules
and guidelines to govern the music they create, most notably the
Common Practice Period of Western music spanning the 17th to early
20th centuries. These rule systems are seldom absolute, and indeed
deliberate breaking the rules is often part of the aesthetic, but they
roughly constrain the music they apply to and give it a common form
and sound.

@@

Starting in the 20th century computers have become ubiquitous in
music in every area including sound sythesis, composition and
production (\citep{roads-tutorial}).

>>>>

Edgar Var\`{e}se describes music as ``organized sound'', and
throughtout history cultures have created and applied systems of rules
and guidelines to govern the music they create, most notably the
Common Practice Period of Western music spanning the 17th to early
20th centuries. These rule systems are seldom absolute, and indeed
deliberate breaking of the rules is often part of the aesthetic, but they
roughly constrain the music they apply to and give it a common form
and sound.

@@

Starting in the 20th century, computers have become ubiquitous in
music in every area, including sound sythesis, composition and
production (\citep{roads-tutorial}).
